---
title: "summaryrow Gallery"
author: "Andy Merlino"
date: "2016-04-02"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{summaryrow Gallery}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### load packages and data
`insurance_data` is sample data provided by the `summaryrow` package.

```{r data, results='asis'}
library(knitr) # for quick tables
library(summaryrow)

# create reported percentage column
insurance_data$reported_pct <- insurance_data$reported / insurance_data$ultimate

kable(insurance_data)
```

### add a totals summary row
```{r, results="asis"}
table_1 <- insurance_data %>% totals_row(cols = 2:4)

kable(table_1)
```

### include a totals row label

Additionally use the `fill` argument to set the fill value supplied in summary row columns not specified in the `cols` argument.  The default is `NA`.

```{r, results="asis"}
table_2 <- insurance_data %>% 
             totals_row(cols = 2:4, label_col = 1, label = "Totals:", fill = "")

kable(table_2)
```

### add an averges row
```{r, results="asis"}
table_3 <- insurance_data %>% 
             averages_row(cols = 5, label_col = 1, label = "Averages:")

kable(table_3)
```

### make a totals and an averages row
```{r, results="asis"}
table_4 <- insurance_data %>% 
             totals_row(cols = 2:4, label_col = 1, label = "Totals 2 yr:") %>%
             averages_row(cols = 5, label_col = 1, label = "Averages:")

kable(table_4)
```

### make one row with totals and averages
```{r, results="asis"}
table_5 <- insurance_data %>% 
             totals_row(cols = 2:4) %>%
             averages_row(cols = 5, label_col = 1, label = "Totals/Averages:", 
                          new_row = FALSE)

kable(table_5)
```

### make a totals row including only the last 2 years
```{r, results="asis"}
table_6 <- insurance_data %>% 
             totals_row(cols = 2:4, label_col = 1, label = "2 Yr Totals:", 
                        rows = 2:3)

kable(table_6)
```

### make two different totals rows
```{r, results="asis"}
table_7 <- insurance_data %>%
             totals_row(cols = 2:4, label_col = 1, label = "2 Yr Totals:", 
                        rows = 2:3) %>%
             totals_row(cols = 2:4, label_col = 1, label = "Totals:")
             

kable(table_7)
```

### putting totals and averages together
```{r, results="asis"}
table_8 <- insurance_data %>% 
             totals_row(cols = 2:4) %>%
             averages_row(cols = 5, label_col = 1, label = "Totals/Averages:", 
                          new_row = FALSE) %>%
             totals_row(cols = 2:4, rows = 2:3) %>%
             averages_row(cols = 5, label_col = 1, label = "2 Yr Totals/Averages:", 
                          rows = 2:3, new_row = FALSE)

kable(table_8)
```

### adding new columns with summary row info
```{r, results="asis"}
library(dplyr, warn.conflicts = FALSE)
table_9 <- insurance_data %>% 
             totals_row(cols = 2:4, label_col = 1, label = "Totals:") %>%
             averages_row(cols = 5, label_col = 1, label = "Totals/Averages:", 
                          new_row = FALSE) %>%
             dplyr::mutate(loss_cost = ultimate / exposure)

kable(table_9)
```

### now to format those columns
```{r, results="asis", eval = TRUE}
table_9 <- insurance_data %>% 
             totals_row(cols = 2:4, label_col = 1, label = "Totals:") %>%
             averages_row(cols = 5, label_col = 1, label = "Totals/Averages:", 
                          new_row = FALSE)

# add some new columns
table_9$loss_cost <- table_9$ultimate / table_9$exposure
table_9$reported_pct <- table_9$reported / table_9$ultimate

table_9 <- table_9 %>%
             format_numeric(cols = 2, digits = 0) %>%
             format_currency(cols = 3:4, digits = 0) %>%
             format_percent(cols = 5, digits = 2) %>%
             format_numeric(cols = 6, digits = 3) %>%
             format_origin(cols = 1, eval = "2017")

kable(table_9)
```